Singapore's Public Housing Affordability

### 2023-11-06 datastory.qmd
Update datastory.qmd

```{r, eval=TRUE,echo=FALSE, message=FALSE, warning=FALSE}
# Load the required libraries
library(tidyverse)
library(tidyr)
library(ggplot2)
library(scales)
```

```{r, eval=TRUE,echo=FALSE}
# Load the datasets
data1999 <- read.csv("docs/src/data/ResaleFlatPrices1999.csv")
data2022 <- read.csv("docs/src/data/ResaleFlatPrices2022.csv")

>>>>

```{r, eval=TRUE,echo=FALSE, message=FALSE, warning=FALSE}

library(tidyverse)
library(tidyr)
library(ggplot2)
library(scales)
```

```{r, eval=TRUE,echo=FALSE}
data1999 <- read.csv("docs/src/data/ResaleFlatPrices1999.csv")
data2022 <- read.csv("docs/src/data/ResaleFlatPrices2022.csv")
